Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-11-13 plos/main.tex
Make minor final adjustments pointed out by PLOS.
Add affiliations that PLOS are happy with.

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline
{ Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma }
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Marc Harper\textsuperscript{1\Yinyang},
Vincent Knight\textsuperscript{2*\Yinyang},
Martin Jones\textsuperscript{3\ddag},
Georgios Koutsovoulos\textsuperscript{4\ddag},
Nikoleta E. Glynatsi\textsuperscript{2\ddag},
Owen Campbell\textsuperscript{5\ddag},
\\
\bigskip
\textbf{1} Google Inc., Mountain View, CA, USA
\\
\textbf{2} Cardiff University, School of Mathematics, UK
\\
\textbf{3} Python for biologist (\url{https://pythonforbiologists.com})
\\
\textbf{4} INRA, Université Côte d‘Azur, CNRS, ISA, France
\\
\textbf{5} Axelrod-Python Project
\\
\bigskip

@@

\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006b}
\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006b}

@@

\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006b}

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline
{ Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma }
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Marc Harper\textsuperscript{1\Yinyang},
Vincent Knight\textsuperscript{2*\Yinyang},
Martin Jones\textsuperscript{3\ddag},
Georgios Koutsovoulos\textsuperscript{4\ddag},
Nikoleta E. Glynatsi\textsuperscript{2\ddag},
Owen Campbell\textsuperscript{5\ddag},
\\
\bigskip
\textbf{1} Google Inc., Mountain View, CA, USA
\\
\textbf{2} Cardiff University, School of Mathematics, Cardiff, UK
\\
\textbf{3} Independent Researcher, Edinburgh, UK
\\
\textbf{4} INRA, Universit\'{e} C\^{o}te d'Azur, CNRS, ISA, Nice, France
\\
\textbf{5} Independent Researcher, Chester, UK
\\
\bigskip

@@

\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006}
\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006}

@@

\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006}
